E1: ENRON Sentiment

### 2016-03-25 paper/paper.tex
up

\section{Experiment}
\label{sec:exp}
In this section we briefly explain the experiment run in order to obtain our results.
After running the setup described in Section~\ref{sec:p-s}, we collect the output data.
Then, we perform a post processing step in which we firstly resample the time series on a weekly (i.e., 7 days) basis using the average as aggregation function.
Moreover, we apply an interpolation function (i.e., polynomial, $4^{th}$ order) to smooth out our time series.
The result is shown in Figure~\ref{fig:sentiment_vs_stock}.

@@

>>>>

\section{Experiment}
\label{sec:exp}
In this section we briefly explain the experiment run in order to obtain our results.
After running the setup described in Section~\ref{sec:p-s}, we collect the output data.
Then, we perform a post processing step in which we firstly resample the time series on a weekly (i.e., 7 days) basis using the average as aggregation function.
Moreover, we apply an interpolation function (i.e., polynomial, $4^{th}$ order) to smooth out our time series.
The result is shown in Figure~\ref{fig:sentiment_vs_stock} where we can notice the dramatic drop of the stock values by the end of 2001.
Although the sentiment value seems not to be strongly affected by the stock's drop, we point out it has a decreasing overall trend.
Indeed, the Pearson correlation  coefficient between the stock price and the sentiment time series is some $0.28$.

@@

Surprisingly, the distribution of sentiment values, shown in Figure~\ref{fig:sentiment_dist_hist}, does not show a significant standard deviation ($0.12$) over the considered time period.
This might be due to either low sentiment-annotation quality by the employed library, or most likely to some inconsistencies in the emails parsing task.
